Machine learning enhanced empirical potentials for metals and alloys

### 2020-04-20 doc/papers/ml-eam/manuscript.tex
Minor update.

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Abstract
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{abstract}
Interatomic potential or force-field plays a vital role in simulating materials. 
Empirical potentials like the embedded atom method (EAM) and its variant 
angular-dependent potential (ADP) have proven successful in modeling many 
metals qualitatively. In the past few years, machine learning has became the 
key approach for modeling interatomic interactions. Powered by big data and 
efficient optimizers, machine learning interatomic potentials can generally 
approximate to the first-principles accuracy. In this works, we successfully 
developed a route to express EAM and ADP within machine learning framework in 
highly-vectorizable form and further enhanced the potentials with physical 
constraints. Machine learning can significantly boost their performances with 
few training data. 
For energy and force 
predictions, machine learned EAM and ADP can be almost as accurate as the 
spectral neighbor analysis potential (SNAP) on the fcc Ni, bcc Mo and Mo-Ni 
alloy systems, while the molecular dynamics simulations performed by the later 
approach is nearly 1000 times slower. Machine learned EAM and ADP can also give 
first-principle accuracy key material properties, such as elastic constants, 
melting temperatures and surface energies. Our results suggest a new and 
systematic route for developing machine learning interatomic potentials. 
\end{abstract}

>>>>

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
% 
% Abstract
%
% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\begin{abstract}
Interatomic potential or force-field plays a vital role in simulating materials. 
Empirical potentials like the embedded atom method (EAM) and its variant 
angular-dependent potential (ADP) have proven successful in modeling many 
metals qualitatively. In the past few years, machine learning has became the 
key approach for modeling interatomic interactions. Powered by big data and 
efficient optimizers, machine learning interatomic potentials can generally 
approximate to the first-principles accuracy. In this works, we successfully 
developed a route to express EAM and ADP within machine learning framework in 
highly-vectorizable form and further enhanced the potentials with physical 
constraints. Machine learning can significantly boost their performances with 
few training data. 
For energy and force 
predictions, machine lear̦ned EAM and ADP can be almost as accurate as the 
spectral neighbor analysis potential (SNAP) on the fcc Ni, bcc Mo and Mo-Ni 
alloy systems, while the molecular dynamics simulations performed by the later 
approach is nearly 1000 times slower. Machine learned EAM and ADP can also give 
first-principle accuracy key material properties, such as elastic constants, 
melting temperatures and surface energies. Our results suggest a new and 
systematic route for developing machine learning interatomic potentials. 
\end{abstract}
